---
title: "Untitled"
author: "Han Xiao"
date: "2/21/2018"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##10.5

##1.Tibbles are data frames, but they tweak some older behaviours to make life a little easier. Tibble will only print a limited number of rows and show the class on top of each column.
```{r}
library(tidyverse)
library(foreign)
library(stringr)
library(plyr)
library(reshape2)
mtcars
```

##2.
Using dollar sign a data.frame will partially complete the column.  This saves a few keystrokes, but can result in accidentally using a different variable than you thought you were using.
With data.frames, with [ the type of object that is returned differs on the number of columns. If it is one column, it won’t return a data.frame, but instead will return a vector. With more than one column, then it will return a data.frame. This is fine if you know what you are passing in, but suppose you did df[ , vars] where vars was a variable. Then you what that code does depends on length(vars) and you’d have to write code to account for those situations or risk bugs.
```{r}
#df <- data.frame(abc = 1, xyz = "a")
#df$x
#df[, "xyz"]
#df[, c("abc", "xyz")]

#tbl <- as_tibble(df)
#tbl$x
#tbl[, "xyz"]
#tbl[, c("abc", "xyz")]

```


##3.
You can use the double bracket, like df[[var]]. You cannot use the dollar sign, because df$var would look for a column named var.

##4.
```{r}
#annoying <- tibble(
#  `1` = 1:10,
#  `2` = `1` * 2 + rnorm(length(`1`))
#)

#annoying[["1"]]
#annoying$`1`
#ggplot(annoying, aes(x = `1`, y = `2`)) +
#  geom_point()
#annoying[["3"]] <- annoying$`2` / annoying$`1`
#annoying <- rename(annoying, one = `1`, two = `2`, three = `3`))
#glimpse(annoying)
```

##5.It converts named vectors to a data frame with names and values
```{r}
#enframe(c(a = 1, b = 2, c = 3))

```

##6.The print function for tibbles is in print.tbl_df
The option n_extra determines the number of extra columns to print information for.

##12.6.1
```{r}
#who1 <- who %>%
#  gather(new_sp_m014:newrel_f65, key = "key", value = "cases", na.rm = TRUE)
#glimpse(who1)

#who2 <- who1 %>%
# mutate(key = stringr::str_replace(key, "newrel", "new_rel"))

#who3 <- who2 %>%
#  separate(key, c("new", "type", "sexage"), sep = "_")
#who3

#who3 %>%
#  count(new)
#count(who$new)

#who4 <- who3 %>%
#  select(-new, -iso2, -iso3)

#who5 <- who4 %>%
#  separate(sexage, c("sex", "age"), sep = 1)
#who5

```

##1

So it appears that either a country has all its values in a year as non-missing if the WHO collected data for that country, or all its values are non-missing. So it is okay to treat explicitly and implicitly missing values the same, and we don’t lose any information by dropping them.
```{r}
#who1 %>%
#  filter(cases == 0) %>%
#  nrow()

#gather(who, new_sp_m014:newrel_f65, key = "key", value = "cases") %>%
#  group_by(country, year)  %>%
#  mutate(missing = is.na(cases)) %>%
#  select(country, year, missing) %>%
#  distinct() %>%
#  group_by(country, year) %>%
#  filter(n() > 1)
```

##2
separate emits the warning “too few values”, and if we check the rows for keys beginning with "newrel_", we see that sexage is messing, and type = m014
```{r}
#who3a <- who1 %>%
#  separate(key, c("new", "type", "sexage"), sep = "_")
#filter(who3a, new == "newrel") %>% head()
```

##3
```{r}
#select(who3, country, iso2, iso3) %>%
#  distinct() %>%
#  group_by(country) %>%
#  filter(n() > 1)
```

```{r}
#who5 %>%
#  group_by(country, year, sex) %>%
#  filter(year > 1995) %>%
#  summarise(cases = sum(cases)) %>%
#  unite(country_sex, country, sex, remove = FALSE) %>%
#  ggplot(aes(x = year, y = cases, group = country_sex, colour = sex)) +
#  geom_line()
```


##second part
##1.
```{r}
pew <- read.spss("pew.sav")
pew <- as.data.frame(pew)


religion <- pew[c("q16", "reltrad", "income")]
religion$reltrad <- as.character(religion$reltrad)
religion$reltrad <- str_replace(religion$reltrad, " Churches", "")
religion$reltrad <- str_replace(religion$reltrad, " Protestant", " Prot")
religion$reltrad[religion$q16 == " Atheist (do not believe in God) "] <- "Atheist"
religion$reltrad[religion$q16 == " Agnostic (not sure if there is a God) "] <- "Agnostic"
religion$reltrad <- str_trim(religion$reltrad)
religion$reltrad <- str_replace_all(religion$reltrad, " \\(.*?\\)", "")

religion$income <- c("Less than $10,000" = "<$10k", 
  "10 to under $20,000" = "$10-20k", 
  "20 to under $30,000" = "$20-30k", 
  "30 to under $40,000" = "$30-40k", 
  "40 to under $50,000" = "$40-50k", 
  "50 to under $75,000" = "$50-75k",
  "75 to under $100,000" = "$75-100k", 
  "100 to under $150,000" = "$100-150k", 
  "$150,000 or more" = ">150k", 
  "Don't know/Refused (VOL)" = "Don't know/refused")[religion$income]

religion$income <- factor(religion$income, levels = c("<$10k", "$10-20k", "$20-30k", "$30-40k", "$40-50k", "$50-75k", 
  "$75-100k", "$100-150k", ">150k", "Don't know/refused"))

counts <- count(religion, c("reltrad", "income"))
names(counts)[1] <- "religion"
raw <- dcast(counts, religion ~ income)

table4 <- raw[1:10, 1:11]


a <- gather(data = table4,key = income, value = freq,-religion)
a <- a[order(a$religion),]
a
```

##2.

```{r}
raw <- read.csv("billboard.csv")
raw <- raw[, c("year", "artist.inverted", "track", "time", "date.entered", "x1st.week", "x2nd.week", "x3rd.week", "x4th.week", "x5th.week", "x6th.week", "x7th.week", "x8th.week", "x9th.week", "x10th.week", "x11th.week", "x12th.week", "x13th.week", "x14th.week", "x15th.week", "x16th.week", "x17th.week", "x18th.week", "x19th.week", "x20th.week", "x21st.week", "x22nd.week", "x23rd.week", "x24th.week", "x25th.week", "x26th.week", "x27th.week", "x28th.week", "x29th.week", "x30th.week", "x31st.week", "x32nd.week", "x33rd.week", "x34th.week", "x35th.week", "x36th.week", "x37th.week", "x38th.week", "x39th.week", "x40th.week", "x41st.week", "x42nd.week", "x43rd.week", "x44th.week", "x45th.week", "x46th.week", "x47th.week", "x48th.week", "x49th.week", "x50th.week", "x51st.week", "x52nd.week", "x53rd.week", "x54th.week", "x55th.week", "x56th.week", "x57th.week", "x58th.week", "x59th.week", "x60th.week", "x61st.week", "x62nd.week", "x63rd.week", "x64th.week", "x65th.week", "x66th.week", "x67th.week", "x68th.week", "x69th.week", "x70th.week", "x71st.week", "x72nd.week", "x73rd.week", "x74th.week", "x75th.week", "x76th.week")]
names(raw)[2] <- "artist"

raw$artist <- iconv(raw$artist, "MAC", "ASCII//translit")
raw$track <- str_replace(raw$track, " \\(.*?\\)", "")
names(raw)[-(1:5)] <- str_c("wk", 1:76)
raw <- arrange(raw, year, artist, track)

long_name <- nchar(raw$track) > 20
raw$track[long_name] <- paste0(substr(raw$track[long_name], 0, 20), "...")

table7 <- raw[c(1:3, 6:10), ]


b <- table7%>%gather(key = 'week',value = 'rank',-year,-artist,-time,-track,-date.entered,na.rm = TRUE)

b$week <- as.integer(str_replace_all(b$week, "[^0-9]+", ""))
b <- rename(b,c('date.entered' = 'date'))
b <- b[order(b$artist),]
b
```

